Parallel Multi-objective optimization using co-evolutionary islands and search space overlapping

### 2016-09-13 hpmoon-hpca.tex
Added some changes to add pseudocode for issue #6

\usepackage{moreverb,url,color}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

@@

@@

@@

>>>>

\usepackage{moreverb,url,color}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

@@

\textcolor{red}{Pseudo-code of the proposed algorithms is described in Figure \ref{fig:pseudo}.}

\begin{algorithm}[htb]

\begin{algorithmic}
\STATE FOR EACH ISLAND
\STATE population $\gets$ initialisePopulation()
\WHILE {stopping criterion not met}
    \STATE parents $\gets$ selection(population)
    \FOR each 2 chromosome in parents
    	\STATE children  $\gets$ parents

    \STATE offspring $\gets$ recombination(parents)
    \STATE offspring $\gets$ mutation(offspring)
    \STATE O $\gets$ offspring.size {\em //O is also equal to the number of parents selected}
    \STATE population $\gets$ population + offspring

    \IF {time to migrate}
      \STATE migrants $\gets$ selectMigrants(population)
      \STATE remoteBuffer.send(migrants)
    \ENDIF

    \IF {localBuffer.size $\neq$ zero}
      \STATE immigrants $\gets$ localBuffer.read()
      \STATE I $\gets$ immigrants.size()
      \STATE population $\gets$ population + immigrants
    \ENDIF

    \IF {localBuffer.size $\neq$ zero}
      \STATE population $\gets$ population + localBuffer.read()
    \ENDIF
    \STATE population $\gets$ population - population.getTheWorst(O + I)
\ENDWHILE

\STATE SEND FRONT TO SERVER
\STATE RETURN NEW FRONT CO ALL ISLANDS

\end{algorithmic}

\caption{Pseudo-code of the used EA: a distributed NSGA-II algorithm }
\label{alg:EA}
\end{algorithm}

@@

\subsection{Benchmark problems}
\textcolor{red}{The first part of the experiments...}

@@

\subsection{Real problem}
\textcolor{red}{A real problem has also been used.}
